Output Summary

### 2023-10-19 03-post-process/ms-content/ms-content.Rmd
Update manuscript content figures
* Include placeholder for map
* Add a model fit summary figure
* Include a table that may better present the "no fall migrants" analysis
* Include some minor aesthetic changes

---
output: 
  pdf_document:
    keep_tex: true
params:
  scenario:
    label: "Scenario"
    value: "base_vlong"
    input: text
  thin_percent:
    label: "Proportion of Posterior Samples to Retain?"
    value: 1
    input: numeric
  include_sim_years:
    value: FALSE
  beta_fig:
    value: TRUE
  relationship_fig:
    value: TRUE
  no_fall_fig:
    value: TRUE
  no_fall_tab:
    value: TRUE
  surv_compare_fig:
    value: TRUE
  apportion_compare_fig:
    value: TRUE
  corr_compare_fig:
    value: TRUE
  WUL_change_fig:
    value: TRUE
  obs_vs_fit_fig:
    value: TRUE
  time_table:
    value: TRUE
header-includes:
  - \usepackage{sansmathfonts}
  - \usepackage{helvet}
  - \renewcommand{\rmdefault}{\sfdefault}
  - \usepackage[labelfont={bf,sc},labelsep=period]{caption}
  - \captionsetup{width=\textwidth}
  - \usepackage{floatrow}
  - \floatsetup[figure]{style=plaintop}
  - \floatsetup[table]{style=plaintop}
editor_options: 
  chunk_output_type: console
---

@@

```{r plot-settings}
solid_col = "grey30"
tranp_col = alpha(solid_col, 0.25)
pt_cex = 1.3
```

```{r captions}
beta_caption = "
  Estimated relationship between parr capacity and weighted usable habitat length.
  Darker grey/thicker error bars represent 80% credible regions and lighter grey/thinner error bars represent 95% credible regions.
"

@@

@@

```{r relationship-fig, fig.width = 7.2, fig.height = 9, fig.cap = msdown::prep_caption(relationship_caption), time_it = TRUE, eval = params$relationship_fig}
solid_col = "grey30"
solid_col2 = "black"
tranp_col = alpha(solid_col, 0.25)
pt_cex = 1.3

@@

\clearpage

\clearpage

>>>>

---
output: 
  pdf_document:
    keep_tex: true
params:
  scenario:
    label: "Scenario"
    value: "new-wul_vlong"
    input: text
  thin_percent:
    label: "Proportion of Posterior Samples to Retain?"
    value: 1
    input: numeric
  include_sim_years:
    value: FALSE
  map_fig:
    value: TRUE
  diagram_fig:
    value: TRUE
  beta_fig:
    value: TRUE
  relationship_fig:
    value: TRUE
  no_fall_fig:
    value: TRUE
  no_fall_tab:
    value: TRUE
  surv_compare_fig:
    value: TRUE
  apportion_compare_fig:
    value: TRUE
  corr_compare_fig:
    value: TRUE
  WUL_change_fig:
    value: TRUE
  obs_vs_fit_fig:
    value: TRUE
  time_table:
    value: FALSE
header-includes:
  - \usepackage{sansmathfonts}
  - \usepackage{helvet}
  - \renewcommand{\rmdefault}{\sfdefault}
  - \usepackage[labelfont={bf,sc},labelsep=period]{caption}
  - \captionsetup{width=\textwidth}
  - \usepackage{floatrow}
  - \floatsetup[figure]{style=plaintop}
  - \floatsetup[table]{style=plaintop}
editor_options: 
  chunk_output_type: console
---

@@

```{r plot-settings}
solid_col = "grey30"
solid_col2 = "black"
tranp_col = alpha(solid_col, 0.25)
pt_cex = 1.3
```

```{r captions}
map_caption = "
  Placeholder for a map figure. The map should show at least: Grande Ronde basin with relevant tributaries, locations of weirs and screw traps, inset map showing region of US covered.
"

diagram_caption = "
  Schematic of the primary states and transitions among states that are captured in the state-space life cycle model for Grande Ronde spring Chinook salmon.
"

beta_caption = "
  Estimated relationship between parr capacity and weighted usable habitat length.
  Darker grey/thicker error bars represent 80% credible regions and lighter grey/thinner error bars represent 95% credible regions.
"

@@

```{r map-fig, fig.width = 7.2, fig.height = 5, fig.cap = msdown::prep_caption(map_caption), eval = params$map_fig}
par(mar = rep(0.25, 4), ljoin = "mitre")
plot(1,1, xlim = c(0,1), ylim = c(0,1), type = "n", axes = FALSE, ann = FALSE)
text(x = 0.5, y = 0.5, "MAP\nPLACEHOLDER", font = 2, cex = 3)
box(lwd = 4)
```

\begin{figure}[H]
{\centering \includegraphics[width=1\linewidth,]{../../100-math-description/GR-sslcm-diagram.pdf}}
\caption{Schematic of the primary states and transitions among states that are captured in the state-space life cycle model for Grande Ronde spring Chinook salmon.}
\label{fig:diagram}
\end{figure}

@@

```{r relationship-fig, fig.width = 7.2, fig.height = 9, fig.cap = msdown::prep_caption(relationship_caption), time_it = TRUE, eval = params$relationship_fig}

@@
